---
title: "Education Graphing"
output: html_notebook
---

Code for the graphs appearing in the Education section of the GLP website.
```{r "setup", include=FALSE}
require("knitr")
opts_knit$set(root.dir = "C:/Users/Harrison Kirby/Desktop/GLP/glp_website")
```

Load libraries
```{r libraries, message = FALSE}
library(showtext)
library(classInt)
library(ggthemes)
library(reshape2)
library(leaflet)
library(rgdal)
library(htmlwidgets)
library(RColorBrewer)
library(tidyverse)
library(magrittr)
library(wesanderson)
```

Load graphing functions and fonts
```{r}
source("graphing_functions.R")

font.add("Museo Sans 300", "C:/Users/Harrison Kirby/Desktop/GLP/MuseoSans_300.otf")
font.add("Museo Sans Italic", "C:/Users/Harrison Kirby/Desktop/GLP/MuseoSans_300_Italic.otf")
```

Create new directories
```{r}
if(!dir.exists("Images")){
  dir.create("Images")
}
if(!dir.exists("Images/Edu_Images")){
  dir.create("Images/Edu_Images")
}
if(!dir.exists("Images/Maps")){
  dir.create("Images/Maps")
}
if(!dir.exists("Images/Maps/edu_maps")){
  dir.create("Images/Maps/edu_maps")
}
```

Read data and filter to 2015
```{r data}
educ_data = read_csv("output data/education_data_fips.csv")
educ_data_15 <- educ_data %>% filter(year == 2015)

naep_data <- read_csv("output data/education_data_naep.csv")
ky_ed_data <- read_csv("output data/education_data_ky.csv")
```

Filter datasets to students in JCPS and break down metrics by race/ethnicity. Tidy data so that each row contains one year and one race/ethnicity.
```{r}
#ACT
jeff_eth_act <- ky_ed_data %>%
  filter(dist_name == "Jefferson County")%>%
  select(year, white_composite_score, african_american_composite_score,
         asian_composite_score, hispanic_composite_score)%>%
  gather(white_composite_score:hispanic_composite_score, key = "var",
         value = "value")%>%
  arrange(var)
jeff_eth_act$var <- factor(jeff_eth_act$var, levels = unique(jeff_eth_act$var))


#CCR
jeff_eth_ccr <- ky_ed_data %>%
  filter(dist_name == "Jefferson County")%>%
  select(year, white_pct_ccr, african_american_pct_ccr,
         asian_pct_ccr, hispanic_pct_ccr)%>%
  gather(white_pct_ccr:hispanic_pct_ccr, key = "var", value = "value")%>%
  arrange(var)
jeff_eth_ccr$var <- factor(jeff_eth_ccr$var, levels = unique(jeff_eth_ccr$var))


#Kindergarten Preparedness
jeff_eth_kscreen <- ky_ed_data %>%
  filter(dist_name == "Jefferson County")%>%
  select(year, white_kind_ready, african_american_kind_ready, 
         asian_kind_ready, hispanic_kind_ready)%>%
  gather(white_kind_ready:hispanic_kind_ready, key = "var", value = "value")%>%
  arrange(var)%>%
  filter(value >= 0)
jeff_eth_ccr$var <- factor(jeff_eth_ccr$var, levels = unique(jeff_eth_ccr$var))


#Graduation Rate
jeff_eth_grad_rate <- ky_ed_data %>%
  filter(dist_name == "Jefferson County")%>%
  select(year, white_cohort_grad_rate, african_american_cohort_grad_rate,
         asian_cohort_grad_rate, hispanic_cohort_grad_rate)%>%
  gather(white_cohort_grad_rate:hispanic_cohort_grad_rate, key = "var", value = "value")%>%
  arrange(var) %>%
  filter(value >= 0)
jeff_eth_ccr$var <- factor(jeff_eth_ccr$var, levels = unique(jeff_eth_ccr$var))
```

Plot ranking graphs
```{r, message = FALSE}
setwd("Images/Edu_Images")

showtext.auto()

jpeg("edu_under_5_pov_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "under_5_per",
  order = "Ascending",
  plot_title = "Children Under 5 in Poverty, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B17001"
)
dev.off()

jpeg("edu_five_to_17_pov_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "five_to_17_per",
  order = "Ascending",
  plot_title = "Children Ages 5 to 17 in Poverty, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B17001"
)
dev.off()

jpeg("edu_child_pov_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "child_per",
  order = "Ascending",
  plot_title = "Child Poverty, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B17001"
)
dev.off()

jpeg("edu_bach_plus_all_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(educ_data_15,
  "bach_plus_per_all",
  plot_title = "Bachelor's Degree or Higher, All Races, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002")
dev.off()

jpeg("edu_bach_plus_black_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "bach_plus_per_black",
  plot_title = "Bachelor's Degree or Higher, Black, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002B"
)
dev.off()

jpeg("edu_25_64_assoc_plus_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "per_25_64_assoc_plus",
  plot_title = "Associate's Degree or Higher, Ages 25-64, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001"
)
dev.off()

jpeg("edu_25_64_bach_plus_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "per_25_64_bach_plus",
  plot_title = "Bachelor's Degree or Higher, Ages 25-64, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001"
)
dev.off()

jpeg("edu_25_64_grad_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "per_25_64_grad",
  plot_title = "Graduate Degree, Ages 25-64, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001"
)
dev.off()

jpeg("edu_25_34_assoc_plus_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "per_25_34_assoc_plus",
  plot_title = "Associate's Degree or Higher, Ages 25-34, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001"
)
dev.off()

jpeg("edu_25_34_bach_plus_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "per_25_34_bach_plus",
  plot_title = "Bachelor's Degree or Higher, Ages 25-34, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001"
)
dev.off()

jpeg("edu_25_34_grad_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "per_25_34_grad",
  plot_title = "Graduate Degree, Ages 25-34, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001"
)
dev.off()

jpeg("edu_bach_plus_hispanic_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "bach_plus_per_hispanic",
  plot_title = "Bachelor's Degree or Higher, Hispanic, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002I"
)
dev.off()

jpeg("edu_bach_plus_white_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "bach_plus_per_white",
  plot_title = "Bachelor's Degree or Higher, White, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002A"
)
dev.off()

jpeg("edu_enrolled_3_4_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "enrolled_3_4",
  plot_title = "Children ages 3 and 4 enrolled in preschool, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table S1401"
)
dev.off()

jpeg("edu_per_high_wage_ranking.jpg", 900, 600, res = 100)
rank_and_nb_group(
  educ_data_15,
  "per_high_wage",
  plot_title = "Population in High Wage Occupations, 2015",
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table S2401"
)
dev.off()

showtext.auto(FALSE)
```

Create education trendline graphs
```{r}
setwd("Images/Edu_Images")

showtext.auto()

jpg("edu_under_5_pov_trendline.png", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "under_5_per",
  plot_title = "Children Under 5 in Poverty",
  rollmean = 3, 
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B17001")
dev.off()

jpeg("edu_five_to_17_pov_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "five_to_17_per", 
  plot_title = "Children Ages 5 to 17 in Poverty",
  rollmean = 3,
  xmin = 2005, 
  xmax = 2015, 
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B17001")
dev.off()

jpeg("edu_child_pov_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "child_per",
  plot_title = "Child Poverty", 
  rollmean = 3, 
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B17001")
dev.off()

jpeg("edu_bach_plus_all_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "bach_plus_per_all",
  plot_title = "Bachelor's Degree or Higher, All Races",
  rollmean = 5,
  xmin = 2005,
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002")
dev.off()

jpeg("edu_bach_plus_black_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data,
  "bach_plus_per_black",
  plot_title = "Bachelor's Degree or Higher, Black",
  rollmean = 5,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002B")
dev.off()

jpeg("edu_25_64_assoc_plus_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data,
  "per_25_64_assoc_plus",
  plot_title = "Associate's Degree or Higher, Ages 25-64",
  rollmean = 3, 
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001")
dev.off()

jpeg("edu_25_64_bach_plus_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data,
  "per_25_64_bach_plus",
  plot_title = "Bachelor's Degree or Higher, Ages 25-64",
  rollmean = 3,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001")
dev.off()

jpeg("edu_25_64_grad_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data,
  "per_25_64_grad",
  plot_title = "Graduate Degree, Ages 25-64",
  rollmean = 3,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001")
dev.off()

jpeg("edu_25_34_assoc_plus_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "per_25_34_assoc_plus",
  plot_title = "Associate's Degree or Higher, Ages 25-34",
  rollmean = 3,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001")
dev.off()

jpeg("edu_25_34_bach_plus_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "per_25_34_bach_plus",
  plot_title = "Bachelor's Degree or Higher, Ages 25-34",
  rollmean = 3,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001")
dev.off()

jpeg("edu_25_34_grad_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "per_25_34_grad",
  plot_title = "Graduate Degree, Ages 25-34",
  rollmean = 3,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15001")
dev.off()

jpeg("edu_bach_plus_hispanic_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data,
  "bach_plus_per_hispanic",
  plot_title = "Bachelor's Degree or Higher, Hispanic",
  rollmean = 5,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002I")
dev.off()

jpeg("edu_bach_plus_white_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "bach_plus_per_white",
  plot_title = "Bachelor's Degree or Higher, White",
  rollmean = 5,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table B15002A")
dev.off()

jpeg("edu_enrolled_3_4_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "enrolled_3_4",
  plot_title = "Children ages 3 and 4 enrolled in preschool",
  rollmean = 5,
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table S1401")
dev.off()

jpeg("edu_per_high_wage_trendline.jpg", 900, 600, res = 100)
graph_trendline(
  educ_data, 
  "per_high_wage",
  plot_title = "Population in High Wage Occupations",
  rollmean = 3, 
  xmin = 2005, 
  xmax = 2015,
  caption_text = "Source: Greater Louisville Project 
                  Data from the American Community Survey, Table S2401")
dev.off()

jpeg("edu_ccr_ethnicity_trendline.jpg", 900, 600, res = 100)
ky_ed_data_long_trendline(
  jeff_eth_ccr,
  break_settings = seq(2012, 2016, 2),
  xmin = 2012,
  xmax = 2016,
  plot_title = "College and Career Readiness by Ethnicity, JCPS",
  labels = c("African American", "Asian", "Hispanic", "White"),
  y_title = "Percent",
  color_pal = wes_palette("Moonrise2"),
  caption = "Source: Greater Louisville Project
             Data from Kentucky Department of Education School Report Card"
)
dev.off()


jpeg("edu_act_ethnicity_trendline.jpg", 900, 600, res = 100)
ky_ed_data_long_trendline(
  jeff_eth_act,
  break_settings = seq(2012, 2016, 2),
  xmin = 2012,
  xmax = 2016,
  plot_title = "ACT Scores by Ethnicity, JCPS",
  labels = c("African American", "Asian", "Hispanic", "White"),
  y_title = "Composite Score",
  color_pal = wes_palette("Moonrise2"),
  caption = "Source: Greater Louisville Project
             Data from Kentucky Department of Education School Report Card"
)
dev.off()


jpeg("edu_grad_rate_ethnicity_trendline.jpg", 900, 600, res = 100)
ky_ed_data_long_trendline(
  jeff_eth_grad_rate,
  break_settings = seq(2013, 2016, 2),
  xmin = 2013,
  xmax = 2016,
  plot_title = "Four Year Graduation Rate by Ethnicity, JCPS",
  labels = c("African American", "Asian", "Hispanic", "White"),
  y_title = "Four Year Graduation Rate",
  color_pal = wes_palette("Moonrise2"),
  caption = "Source: Greater Louisville Project
             Data from Kentucky Department of Education School Report Card"
)
dev.off()


jpeg("edu_kindergarten_prep_ethnicity_trendline.jpg", 900, 600, res = 100)
ky_ed_data_long_trendline(
  jeff_eth_kscreen,
  break_settings = seq(2014, 2016, 2),
  xmin = 2014,
  xmax = 2016,
  plot_title = "Kindergarten Preparedness by Ethnicity, JCPS",
  labels = c("African American", "Asian", "Hispanic", "White"),
  y_title = "Percent",
  color_pal = wes_palette("Moonrise2"),
  caption = "Source: Greater Louisville Project
             Data from Kentucky Department of Education School Report Card"
)
dev.off()


jpeg("edu_act_trendline.jpg", 900, 600, res = 100)
graph_trendline_ky_ed(
  ky_ed_data,
  "all_students_composite_score",
  plot_title = "ACT Composite Scores",
  y_title = "Composite Score",
  xmin = 2012,
  xmax = 2016,
  break_settings = seq(2012, 2016, 2),
  caption = "Source: Greater Louisville Project
             Data from Kentucky Department of Education School Report Card"
)
dev.off()

jpeg("edu_ccr_trendline.jpg", 900, 600, res = 100)
graph_trendline_ky_ed(
  ky_ed_data,
  "all_students_pct_ccr",
  plot_title = "College and Career Readiness",
  y_title = "Percent",
  xmin = 2012,
  xmax = 2016,
  break_settings = seq(2012, 2016, 2),
  caption = "Source: Greater Louisville Project 
             Data from Kentucky Department of Education School Report Card"
)
dev.off()

jpeg("edu_kindergarten_prep_trendline.jpg", 900, 600, res = 100)
graph_trendline_ky_ed(
  ky_ed_data,
  "all_students_kind_ready",
  plot_title = "Kindergarten Preparedness",
  y_title = "Percent",
  xmin = 2014,
  xmax = 2016,
  break_settings = seq(2014, 2016, 2),
  caption = "Source: Greater Louisville Project
             Data from Kentucky Department of Education School Report Card"
)
dev.off()

jpeg("edu_graduation_rate_trendline.jpg", 900, 600, res = 100)
graph_trendline_ky_ed(
  ky_ed_data,
  "all_students_cohort_grad_rate",
  plot_title = "Graduation Rate",
  y_title = "Percent",
  xmin = 2013,
  xmax = 2016,
  break_settings = seq(2013, 2016, 2),
  caption = "Source: Greater Louisville Project
             Data from Kentucky Department of Education School Report Card"
)
dev.off()

jpeg("edu_naep_reading_trendline.jpg", 900, 600, res = 100)
ky_ed_data_long_trendline(
  naep_data, 
  var = "Jurisdiction", 
  value = "naep_reading_score", 
  break_settings = seq(2009, 2016,2),
  xmin = 2009,
  xmax = 2015, 
  plot_title = "NAEP 4th Grade Reading Score",
  labels = c("JCPS", "Kentucky School District Mean"),
  y_title = "Composite Score",
  color_pal = c("#00a9b7", "black"),
  caption = "Source: Greater Louisville Project
             Data from National Center for Education Statistics")
dev.off()

jpeg("edu_naep_math_trendline.jpg", 900, 600, res = 100)
ky_ed_data_long_trendline(
  naep_data, 
  var = "Jurisdiction",
  value = "naep_math_score", 
  break_settings = seq(2009, 2016,2),
  xmin = 2009,
  xmax = 2015, 
  plot_title = "NAEP 4th Grade Math Score",
  labels = c("JCPS", "Kentucky School District Mean"),
  y_title = "Composite Score",
  color_pal = c("#00a9b7", "black"),
  caption = "Source: Greater Louisville Project
             Data from National Center for Education Statistics")
dev.off()

showtext.auto(FALSE)
```

Add map data
```{r}
map_data = read_csv("map data/education_map_data.csv", col_types = cols(enrolled_3_4 = col_double()))
map_data[ ,c(3:5, 7:12, 14)] <- map_data[ ,c(3:5, 7:12, 14)]*100

setwd("map data")

map_jc = readOGR("JC Tracts", layer = "JC Tracts",
                 GDAL1_integer64_policy = TRUE)

map_jc@data<-full_join(map_jc@data, map_data, by = c('GEO_ID' = 'Id'))

map_jc@data$tract_num <- substr(map_jc@data$Id2, 6, 11)

map_jc@data$l_line1 <- paste("Tract #:", map_jc@data$tract_num, "in the")
map_jc@data$l_line2 <- paste(map_jc@data$Neighborhood, "neighborhood")


```

Output maps
```{r}
setwd("Images/Maps/edu_maps")

m <- make_map("child_per", name = "Child Poverty", legend_title = "Child<br>Poverty", map_style = "sequential")
saveWidget(m, "edu_child_pov_map.html")

m <- make_map("per_25_64_assoc_plus", name = "Associate Degree or Higher, Ages 25-64", legend_title = "Ages 25 to 64 with<br/>Associate Degree<br/>or higher", units = "Percent")
saveWidget(m, "edu_25_64_assoc_map.html")

m <- make_map("per_25_64_bach_plus", name = "Bachelor's Degree or Higher, Ages 25-64", legend_title = "Ages 25 to 64 with<br/>Bachelor's Degree<br/>or higher", units = "Percent")
saveWidget(m, "edu_25_64_bach_map.html")

m <- make_map("per_25_64_grad", "Graduate Degree, Ages 25-64", legend_title = "Ages 25 to 64 with<br/>Graduate Degree", units = "Percent")
saveWidget(m, "edu_25_64_grad_map.html")

m <- make_map("per_25_34_assoc_plus", name = "Associate Degree or Higher, Ages 25-34", legend_title = "Ages 25 to 34 with<br/>Associate's Degree<br/>or higher", units = "Percent")
saveWidget(m, "edu_assoc_25_34_map.html")

m <- make_map("per_25_34_bach_plus", name = "Bachelor's Degree or Higher, Ages 25-34", legend_title = "Ages 25 to 34 with<br/>Bachelor's Degree<br/>or higher", units = "Percent")
saveWidget(m, "edu_25_34_bach_map.html")

m <- make_map("per_25_34_grad", name = "Graduate Degree, Ages 25-34", legend_title = "Ages 25 to 34 with<br/>Graduate Degree", units = "Percent")
saveWidget(m, "edu_25_34_grad_map.html")

m <- make_map("per_high_wage", "Population in High Wage Occupations",
              legend_title = "Population in<br/>High Wage<br/>Occupations")
saveWidget(m, "edu_per_high_wage_map.html")
```

