---
title: "QOP_pull"
output: html_notebook
---

Code for pulling quality of place data

```{r "setup", include=FALSE}
require("knitr")
opts_knit$set(root.dir = "~/Desktop/glp_website")
```

Loading Libraries
```{r}
library(showtext)
library(reshape2)
library(classInt)
library(ggthemes)
library(tidyverse)
library(magrittr)
```


Necessary Functions
```{r}
pull_peers_MSA<-function(data){
  all.peers<-filter(data, data$CBSA == 24340 | data$CBSA == 41180
                    |data$CBSA == 36420 | data$CBSA == 46140
                    |data$CBSA == 24860 |data$CBSA == 28940
                    |data$CBSA == 13820 |data$CBSA == 26900
                    |data$CBSA == 31140 |data$CBSA == 28140
                    |data$CBSA == 36540 |data$CBSA == 24660
                    |data$CBSA == 16740 |data$CBSA == 18140
                    |data$CBSA == 17140 |data$CBSA == 34980
                    |data$CBSA == 32820 |data$CBSA == 27260
                    |data$CBSA == 39580 |data$CBSA == 19380
                    |data$CBSA == 40060)
  all.peers$baseline<-1
  all.peers$current<-1
  all.peers$baseline[all.peers$CBSA == 24340 | all.peers$CBSA == 41180
                     |all.peers$CBSA == 36420 | all.peers$CBSA == 46140
                     |all.peers$CBSA == 24860 | all.peers$CBSA == 28940]<-0
  all.peers$current[all.peers$CBSA == 27260 | all.peers$CBSA == 39580
                    |all.peers$CBSA == 19380 | all.peers$CBSA == 40060]<-0
  all.peers
}

pull_peers_FIPS <- function(dat){
  all.peers <- subset(dat, dat$FIPS == 1073 | dat$FIPS == 37119
                      |dat$FIPS == 39061 |dat$FIPS == 39049
                      |dat$FIPS == 26081 |dat$FIPS == 37081
                      |dat$FIPS == 45045 |dat$FIPS == 18097
                      |dat$FIPS == 29095 |dat$FIPS == 47093
                      |dat$FIPS == 21111 |dat$FIPS == 47157
                      |dat$FIPS == 47037 |dat$FIPS == 40109
                      |dat$FIPS == 31055 |dat$FIPS == 29189
                      |dat$FIPS == 29510 |dat$FIPS == 40143
                      |dat$FIPS == 12031 |dat$FIPS == 37183
                      |dat$FIPS == 39113 |dat$FIPS == 51760
                      | dat$FIPS == "01073")
  all.peers$baseline <- 1
  all.peers$current <- 1
  all.peers$baseline[all.peers$FIPS==26081|all.peers$FIPS==29189
                     |all.peers$FIPS==29510|all.peers$FIPS==40109
                     |all.peers$FIPS==40143|all.peers$FIPS==45045
                     |all.peers$FIPS==47093]<-0
  all.peers$current[all.peers$FIPS== 12031|all.peers$FIPS==37183|
                      all.peers$FIPS==39113|all.peers$FIPS==51760]<-0
  all.peers
}

cbp_read<-function(folder, starting_year){
  initial_wd <- getwd()
  directory <- paste(initial_wd, folder, sep = "/")
  file_names<-list.files(directory)
  n <- length(file_names)
  y <- starting_year
  for(i in 1:n){
    data<-read_csv(paste(directory,file_names[i], sep = "/"), skip = 0, progress = FALSE)
    data%<>%mutate(FIPS = paste(fipstate, fipscty, sep = ''))
    all.peers <- filter(data, data$FIPS == "01073" |data$FIPS == 37119
                        |data$FIPS == 39061 |data$FIPS == 39049
                        |data$FIPS == 26081 |data$FIPS == 37081
                        |data$FIPS == 45045 |data$FIPS == 18097
                        |data$FIPS == 29095 |data$FIPS == 47093
                        |data$FIPS == 21111 |data$FIPS == 47157
                        |data$FIPS == 47037 |data$FIPS == 40109
                        |data$FIPS == 31055 |data$FIPS == 29189
                        |data$FIPS == 29510
                        |data$FIPS == 40143 |data$FIPS == 39113
                        |data$FIPS == 12031 |data$FIPS == 37183
                        |data$FIPS == 37183 |data$FIPS == 51760)
    all.peers$year <- y
    all.peers$baseline <- 1
    all.peers$current <- 1
    all.peers$baseline[all.peers$FIPS==26081|all.peers$FIPS==29189
                       |all.peers$FIPS==29510|all.peers$FIPS==40109
                       |all.peers$FIPS==40143|all.peers$FIPS==45045
                       |all.peers$FIPS==47093]<-0
    all.peers$current[all.peers$FIPS== 12031|all.peers$FIPS==37183|
                        all.peers$FIPS==39113|all.peers$FIPS==51760]<-0
    y<-y+1
    
    if(i == 1){
      df <- all.peers
    }
    else{
      names(all.peers)<-names(df)
      df<-rbind(df, all.peers)
    }
  }
  df
}

volunteer_read<-function(data){
  df<-read_csv(data, progress = FALSE)
  colnames(df)<-c("RANK", "CITY","STATE","volunteer_pct")
  year = substr(data, 57, 60)
  df$Year = NA
  df$Year = as.numeric(year)
  df%<>%filter(CITY == "Birmingham" | CITY == "Charlotte"|
                 CITY == "Cincinnati" | CITY == "Columbus" |
                 CITY == "Greensboro" | CITY == "Grand Rapids" |
                 CITY == "Greenville" | CITY == "Indianapolis"|
                 CITY == "Kansas City" | CITY == "Knoxville"|
                 CITY == "Louisville" | CITY == "Memphis"|
                 CITY == "Nashville" | CITY == "Oklahoma City"|
                 CITY == "Omaha" | CITY == "St. Louis"|
                 CITY == "Tulsa")
  df$MSA<-NA
  df$MSA[df$CITY == "Birmingham"] = 13820
  df$MSA[df$CITY == "Charlotte"] = 16740
  df$MSA[df$CITY == "Cincinnati"] = 17140
  df$MSA[df$CITY == "Columbus"] = 18140
  df$MSA[df$CITY == "Grand Rapids"] = 24340
  df$MSA[df$CITY == "Greensboro"] = 24660
  df$MSA[df$CITY == "Greenville"] = 24860
  df$MSA[df$CITY == "Indianapolis"] = 26900
  df$MSA[df$CITY == "Kansas City"] = 28140
  df$MSA[df$CITY == "Knoxville"] = 28940
  df$MSA[df$CITY == "Louisville"] = 31140
  df$MSA[df$CITY == "Memphis"] = 32820
  df$MSA[df$CITY == "Nashville"] = 34980
  df$MSA[df$CITY == "Oklahoma City"] = 36420
  df$MSA[df$CITY == "Omaha"] = 36540
  df$MSA[df$CITY == "St. Louis"] = 41180
  df$MSA[df$CITY == "Tulsa"] = 46140
  df$volunteer_pct[substr(df$volunteer_pct,
                          nchar(df$volunteer_pct),
                          nchar(df$volunteer_pct)) == "%"] = substr(df$volunteer_pct[substr(df$volunteer_pct,
                                                                                            nchar(df$volunteer_pct),
                                                                                            nchar(df$volunteer_pct)) == "%"], 1, nchar(df$volunteer_pct)-1)
  df$volunteer_pct = as.numeric(df$volunteer_pct)
  df%<>%select(volunteer_pct, Year, MSA, city = CITY)
  df
}

##using z-scores to identify MPI neighborhoods
NormZ<-function(x){
  (x-mean(x))/sd(x)
}

```

GEOFred Data Analysis
```{r}
house_dat <- read_csv("input data/qp_input_data/all_transactions_house_price_index.csv", skip = 1, progress = FALSE)
burdened_dat <- read_csv("input data/qp_input_data/burdened_households.csv", skip = 1, progress = FALSE)
disconnected_dat <- read_csv("input data/qp_input_data/disconnected youth.csv", skip = 1, progress = FALSE)
home_own_dat <- read_csv("input data/qp_input_data/homeownership_rate.csv", skip = 1, progress = FALSE)
income_inequality_dat <- read_csv("input data/qp_input_data/income_inequality.csv", skip = 1, progress = FALSE)
commute_time_dat <- read_csv("input data/qp_input_data/mean_commuting_time.csv", skip = 1, progress = FALSE)
net_migration_flow_dat <- read_csv("input data/qp_input_data/net_migration_flow.csv", skip = 1, progress = FALSE)
race_dat <- read_csv("input data/qp_input_data/white to nonwhite racial dissimilarity index.csv", skip = 1, progress = FALSE)
median_household_income_dat <- read_csv("input data/qp_input_data/median_household_income.csv", skip = 1)


##pulling peers

#renaming
house_dat <- house_dat %>% rename(FIPS = `Region Code`)
burdened_dat <- burdened_dat %>% rename(FIPS = `Region Code`)
disconnected_dat <- disconnected_dat %>% rename(FIPS = `Region Code`)
home_own_dat <- home_own_dat %>% rename(FIPS = `Region Code`)
income_inequality_dat <- income_inequality_dat %>% rename(FIPS = `Region Code`)
commute_time_dat <- commute_time_dat %>% rename(FIPS = `Region Code`)
net_migration_flow_dat <- net_migration_flow_dat %>% rename(FIPS = `Region Code`)
race_dat <- race_dat %>% rename(FIPS = `Region Code`)
median_household_income_dat <- median_household_income_dat %>% rename(FIPS = `Region Code`)

#pulling
house_dat <- pull_peers_FIPS(house_dat)
burdened_dat <- pull_peers_FIPS(burdened_dat)
disconnected_dat <- pull_peers_FIPS(disconnected_dat)
home_own_dat <- pull_peers_FIPS(home_own_dat)
income_inequality_dat <- pull_peers_FIPS(income_inequality_dat)
commute_time_dat <- pull_peers_FIPS(commute_time_dat)
net_migration_flow_dat <- pull_peers_FIPS(net_migration_flow_dat)
race_dat <- pull_peers_FIPS(race_dat)
median_household_income_dat <- pull_peers_FIPS(median_household_income_dat)



##reformatting
house_dat <- house_dat %>%
  gather(4:24, key = "year", value = "housing_price_index") #4:24 refers to column indexes for all the years

burdened_dat <- burdened_dat %>%
  gather(4:9, key = "year", value = "burdened_households") #4:9 refers to column indexes for all the years

disconnected_dat <- disconnected_dat %>%
  gather(4:10, key = "year", value = "disconnected_youth") #4:10 refers to column indexes for all the years

home_own_dat <- home_own_dat %>%
  gather(4:10, key = "year", value = "home_ownership") #4:10 refers to column indexes for all the years

income_inequality_dat <- income_inequality_dat %>%
  gather(4:9, key = "year", value = "income_inequality") #4:9 refers to column indexes for all the years

commute_time_dat <- commute_time_dat %>%
  gather(4:10, key = "year", value = "commute_time") #4:10 refers to column indexes for all the years

net_migration_flow_dat <- net_migration_flow_dat %>%
  gather(4:8, key = "year", value = "net_migration_flow") #4:8 refers to column indexes for all the years

race_dat <- race_dat %>%
  gather(4:10, key = "year", value = "racial_geography") #4:10 refers to column indexes for all the years

median_household_income_dat <- median_household_income_dat %>%
  gather(4:24, key = "year", value = "median_household_income") #4:24 refers to column indexes for all the years


fred_dat <- full_join(burdened_dat, commute_time_dat, by = c("FIPS", "year",
                                                             "baseline", "current"))
fred_dat <- full_join(fred_dat, disconnected_dat, by = c("FIPS", "year"))
fred_dat <- full_join(fred_dat, home_own_dat, by = c("FIPS", "year"))
fred_dat <- full_join(fred_dat, house_dat, by = c("FIPS", "year"))
fred_dat <- full_join(fred_dat, income_inequality_dat, by = c("FIPS", "year"))
fred_dat <- full_join(fred_dat, net_migration_flow_dat, by = c("FIPS", "year"))
fred_dat <- full_join(fred_dat, race_dat, by = c("FIPS", "year"))

fred_dat <- full_join(fred_dat, median_household_income_dat, by = c("FIPS", "year"))
fred_dat <- pull_peers_FIPS(fred_dat)

fred_dat <- fred_dat %>% select(FIPS, year, baseline, current, 
                                burdened_households, commute_time, disconnected_youth,
                                home_ownership, housing_price_index,
                                income_inequality, net_migration_flow,
                                racial_geography,median_household_income)
fred_dat$FIPS[fred_dat$FIPS == "01073"] = 1073


#current peers
fred_dat$year <- as.numeric(fred_dat$year)
fred_dat$housing_price_index <- as.numeric(fred_dat$housing_price_index)
fred_dat$racial_geography <- as.numeric(fred_dat$racial_geography)
fred_dat$median_household_income <- as.numeric(fred_dat$median_household_income)

#
##Now to give the FIPS codes names
names <- read_csv("input data/FIPS two stl.csv", col_types = cols(FIPS = col_integer()), progress = FALSE)
names$FIPS <- as.character(names$FIPS)
data_named <- left_join(fred_dat, names, by = "FIPS")

##and merge St. Louis city and St. Louis county

data_named$FIPS <- as.numeric(data_named$FIPS)
dat <- data_named %>%
  filter(year > 2004 & year < 2016) %>%
  pull_peers_FIPS(.)%>%
  select(-county, -state) %>%
  group_by(city, year) %>%
  summarise_each(funs(weighted.mean(.,weights))) %>%
  ungroup()

# give St. Louis Merged a new FIPS
dat$FIPS <- as.character(dat$FIPS)
dat$FIPS[dat$city == "St. Louis"] <- "MERGED"
dat$FIPS <- as.factor(dat$FIPS)


population_one_stl<-read_csv("input data/population_data_one_stl.csv", progress = FALSE)
population_one_stl$FIPS <- as.character(population_one_stl$FIPS)
fred_dat <- left_join(dat, population_one_stl, by = c("FIPS", "year"))


fred_dat <- fred_dat %>% 
  mutate(migration_pop = net_migration_flow/population)%>%
  select(-weights)

qp_data_fips<-fred_dat
```

Social Support Analysis
```{r}
#Reading in and tidying data
sc_data_5_6 <- cbp_read("input data/qp_input_data/Social Support 5_6", starting_year = 2005)
sc_data_5_6 %<>% select(naics, FIPS, year, baseline, current, est)

sc_data_7_14 <- cbp_read("input data/qp_input_data/Social Support 7_14", starting_year = 2007)
sc_data_7_14 %<>% select(naics, FIPS, year, baseline, current, est)

sc_data_15 <- read_csv("input data/qp_input_data/cbp15co.txt.zip", progress = FALSE)
sc_data_15$year = 2015
sc_data_15%<>%mutate(FIPS = paste(FIPSTATE, FIPSCTY, sep = ''))%>%
  pull_peers_FIPS(.)%>%
  select(naics = NAICS, FIPS, year, baseline, current, est = EST)

sc_data<-bind_rows(sc_data_5_6, sc_data_7_14)
sc_data<-bind_rows(sc_data, sc_data_15)

#Pull St. Louis out of the Dataset and sum
sc_data_no<-sc_data%>%filter(naics == 813410 | naics == 713950|
                               naics == 713910 | naics == 713940|
                               naics == 711211 | naics == 813110|
                               naics == 813940 | naics == 813930|
                               naics == 813910 | naics == 813920)%>%
  filter(!(FIPS == 29189 | FIPS == 29510))%>%
  group_by(year, FIPS, baseline, current)%>%
  summarize(ss_est = sum(est))

#Sum social support firms for all cities besides St. Louis
stl_sc<-sc_data%>%filter(naics == 813410 | naics == 713950|
                           naics == 713910 | naics == 713940|
                           naics == 711211 | naics == 813110|
                           naics == 813940 | naics == 813930|
                           naics == 813910 | naics == 813920)%>%
  filter(FIPS == 29189 | FIPS == 29510)%>%
  group_by(year, baseline, current)%>%
  summarize(ss_est = sum(est))
stl_sc$FIPS <- NA
stl_sc$FIPS <- "MERGED"

#Add St. Louis back to the dataset
sc_data <- bind_rows(sc_data_no, stl_sc)
sc_data$FIPS[sc_data$FIPS == "01073"] = "1073"

#Combine to QP FIPS data
qp_data_fips<-left_join(qp_data_fips, sc_data, by = c("year","FIPS","baseline","current"))

#Create per 100000 rate from population data in the QP FIPS dataset
qp_data_fips%<>% mutate(ss_est_per_10000 = (ss_est/population)*10000)
```

PCT Population in Core MSA County Analysis
```{r}
#Read in data
fips_core_county_pop<-read_csv("input data/population_data_one_stl.csv", progress = FALSE)

#Create "key" for core FIPS county to MSA
msa_fips_key<-read_csv("input data/qp_input_data/changed_msa_counties.csv", progress = FALSE)
msa_fips_key%<>%pull_peers_FIPS(.)%>%
  distinct(MSA, .keep_all = TRUE)%>%
  select(FIPS, MSA)
msa_fips_key$FIPS[msa_fips_key$MSA == 41180]<- "MERGED"

#Add MSA code
fips_core_county_pop<-left_join(fips_core_county_pop, msa_fips_key, by = "FIPS")
fips_core_county_pop%<>%filter(year >= 2010)%>%
  dplyr::rename(Year = year)

#Tidy MSA Population estimate Data
msa_pop_est<-read_csv("input data/qp_input_data/cbsa-est2016-alldata.csv", n_max = 1581, progress = FALSE)
msa_pop_est%<>%filter(LSAD == "Metropolitan Statistical Area")%>%
  pull_peers_MSA(.)%>%
  select(CBSA, POPESTIMATE2010:POPESTIMATE2015)%>%
  gather(POPESTIMATE2010:POPESTIMATE2015, key = 'Year',value = population_estimate)%>%
  dplyr::rename(MSA = CBSA)

msa_pop_est$Year = substr(msa_pop_est$Year, 12,15)
msa_pop_est$Year = as.numeric(msa_pop_est$Year)

#Combine datasets and create core county pct estimates
fips_core_county_pop<-left_join(fips_core_county_pop, msa_pop_est, by = c("MSA", "Year"))

fips_core_county_pop%<>%mutate(pct_pop_core_county = 100*population/population_estimate)%>%
  dplyr::rename(core_county_pop = population,
                msa_population_estimate = population_estimate,
                year = Year)%>%
  select(FIPS, year, MSA,msa_population_estimate, pct_pop_core_county)
fips_core_county_pop$FIPS <- as.character(fips_core_county_pop$FIPS)

#Combine to QP FIPS data
qp_data_fips<-left_join(qp_data_fips, fips_core_county_pop, by = c("year", "FIPS"))
```

Food Insecurity Analysis
```{r}
#Read in data
food_insec<-read_csv("input data/qp_input_data/GLP counties food insecure_PCT.csv", progress = FALSE)

#Tidy
food_insec%<>%
  pull_peers_FIPS(.)%>%
  dplyr::rename(year = Year)%>%
  select(city, FIPS, year, food_insecure_overall, food_insecure_child)

#Add weights for St. Louis
weights <-
  read_csv(
  "input data/FIPS two stl.csv",
  col_types = cols(FIPS = col_integer()),
  progress = FALSE
  ) 
food_insec<-left_join(food_insec, weights, by = c("city", "FIPS"))
food_insec$FIPS<-as.character(food_insec$FIPS)

#Compute rates for St. Louis
st_lou<-food_insec%>%
  filter(FIPS == "29189" | FIPS == "29510")%>%
  group_by(year, city)%>%
  summarise(food_insecure_overall = weighted.mean(food_insecure_overall, weights),
            food_insecure_child = weighted.mean(food_insecure_child, weights))
st_lou$FIPS<-"MERGED"
st_lou%<>%select(year, city, food_insecure_overall, food_insecure_child, FIPS)

food_insec%<>%select(-c(county, state, weights))%>%
  filter(!(FIPS == 29189 | FIPS == 29510))

#Combine St. Louis back to data set
food_insec <- bind_rows(food_insec, st_lou)

#Combine to QP FIPS data
qp_data_fips<-left_join(qp_data_fips, food_insec, by = c("year", "FIPS", "city"))
```

Food Desert Analysis
```{r}
#Read in Data
fd_data <- read_csv("input data/qp_input_data/food_desert_2015.csv",
              col_types = cols(laasian20 = col_double(),
                               lanhopi20 = col_double(),
                               lanhopi20share = col_double(),
                               laasian20share = col_double(),
                               laaian20share = col_double(),
                               laaian20 = col_double(),
                               laomultir20 = col_double(),
                               laomultir20share = col_double(),
                               lahisp20 = col_double(),
                               lahisp20share = col_double()), progress = FALSE)


#Creating FIPS Codes w/ only the first five digits of tract codes
FIPS <- substr(fd_data$CensusTract, 1,5)
FIPS <- as.numeric(FIPS)
fd_data$FIPS <- NA
fd_data$FIPS <- FIPS

#Obtain Total Population
pop <- fd_data %>%
  pull_peers_FIPS(.) %>%
  group_by(FIPS) %>%
  summarise(total_city_pop = sum(POP2010),
            total_city_households = sum(OHU2010))

#Select Data
fd_data<-fd_data%>%
  pull_peers_FIPS(.)%>%
  select(c(CensusTract:LILATracts_Vehicle,LALOWI1_10, LALOWI05_10,
           lahunvhalf, lahunv1,HUNVFlag,LowIncomeTracts,
           FIPS, baseline,current))%>%
  select(-c(GroupQuartersFlag,NUMGQTRS,PCTGQTRS, LILATracts_1And20))

#Add population
fd_data<-inner_join(fd_data, pop, by = "FIPS")

#Hack in St. Louis Population and Household totals
fd_data$FIPS[fd_data$FIPS==29189]<-"MERGED"
fd_data$FIPS[fd_data$FIPS==29510]<-"MERGED"
fd_data$total_city_pop[fd_data$FIPS=="MERGED"] <- 1318248
fd_data$total_city_households[fd_data$FIPS=="MERGED"] <- 546822

#Compute Food Desert Vehicle Statistics
# Number of households who have no vehicle
# and live more than 1/2 a mile away from a supermarket, that also live in
# a low income census tract (per 100,000 households).

#Checking percentages
fd_data <- fd_data %>%
  filter(LowIncomeTracts == 1) %>%
  group_by(FIPS,
           total_city_pop,
           total_city_households,
           current,
           baseline) %>%
  summarise(
    est_food_desert_households = sum(lahunvhalf)
    #Total households without a car and beyond
    #1/2 mile from a supermarket in a Food Desert
    #Census tract determined by vehicle access and
    #1/2 mile
  ) %>%
  mutate(est_food_desert_households_per100000_lowIncTract =
           est_food_desert_households / total_city_households * 100)

# fd_data <- fd_data %>%
#   filter(LowIncomeTracts == 1) %>%
#   group_by(FIPS,
#            total_city_pop,
#            total_city_households,
#            current,
#            baseline) %>%
#   summarise(
#     est_food_desert_households = sum(lahunvhalf)
#     #Total households without a car and beyond
#     #1/2 mile from a supermarket in a Food Desert
#     #Census tract determined by vehicle access and
#     #1/2 mile
#   ) %>%
#   mutate(est_food_desert_households_per100000_lowIncTract =
#            est_food_desert_households / total_city_households * 100000)
#Grocery Store estimates are from a 2010 study. Population estimates are from 2015.
fd_data$year<-2015
fd_data <- ungroup(fd_data)
fd_data%<>%select(-c(total_city_pop,total_city_households, current, baseline))

#Combine to QP FIPS data
qp_data_fips<-left_join(qp_data_fips, fd_data, by = c("FIPS", "year"))
```

County Health Rankings Data Analysis
```{r}
#Reading in Data
chr_df_17 <- read_csv("input data/qp_input_data/2017CHR_CSV_Analytic_Data.csv",
                       col_types = cols(
                       measure_127_value = col_character(),
                       measure_131_value = col_character()
                       )
                      )

chr_df_17 = chr_df_17 %>% rename(FIPS = fipscode) #renaming a variable for use in the function below

chr_df_17 <- pull_peers_FIPS(chr_df_17)
chr_df_17$FIPS[chr_df_17$FIPS == "01073"] <- "1073"


#Selecting QP Variables
chr_df_17 <- chr_df_17 %>%
  select(
    violent_crime = measure_43_value,
    injury_deaths = measure_135_value,
    air_pollution = measure_125_value,
    severe_housing_problems = measure_136_value,
    driving_alone_to_work = measure_67_value,
    FIPS, current, baseline
  )

#Selecting Current Peers only
chr_df_17 <- chr_df_17 %>% filter(current ==1)

name_df <- read_csv("input data/FIPS two stl.csv")
name_df$FIPS <- as.character(name_df$FIPS)

chr_named <- left_join(chr_df_17, name_df, by = "FIPS")
chr_named$FIPS <- as.numeric(chr_named$FIPS)

chr_stl <- chr_named %>%
  select(-county, -state) %>%
  group_by(city) %>%
  summarise_each(funs(weighted.mean(.,weights)), -weights)

# give St. Louis Merged a new FIPS
chr_stl$FIPS <- as.character(chr_stl$FIPS)
chr_stl$FIPS[chr_stl$city == "St. Louis"] <- "MERGED"
chr_stl%<>%select(-c(current, baseline, city))%>%
  mutate(severe_housing_problems = severe_housing_problems*100,
         driving_alone_to_work = driving_alone_to_work*100)
chr_stl$year<-2015

#Combine to QP FIPS data
qp_data_fips<-left_join(qp_data_fips, chr_stl, by = c("year", "FIPS"))

```

MPI Analysis from Competative City Update 2015
```{r}
#Reading in Data
pc_ed_data<-read_csv("input data/qp_input_data/ACS_14_5YR_B23006_with_ann.csv", skip = 1)
pc_ed_data%<>%select(Id2, ed_population = `Estimate; Total:`, 
                less_than_hs = `Estimate; Less than high school graduate:`,
                bachelors_up = `Estimate; Bachelor's degree or higher:`)%>%
  mutate(bachelors_degree = bachelors_up/ed_population,
                no_hs_degree = less_than_hs/ed_population)

pc_health_data<-read_csv("input data/qp_input_data/ACS_14_5YR_S2701_with_ann.csv", skip=1)
pc_health_data%<>%select(Id2, health_population = `Total; Estimate; Total civilian noninstitutionalized population`, 
         uninsured = `Percent Uninsured; Estimate; Total civilian noninstitutionalized population`)
pc_health_data$uninsured = as.numeric(as.character(pc_health_data$uninsured))

pc_low_inc_data<-read_csv("input data/qp_input_data/ACS_14_5YR_C17002_with_ann.csv", skip=1)
pc_low_inc_data%<>%
  select(
    Id2,
    low_inc_population = `Estimate; Total:`,
    less_than_50 = `Estimate; Total: - Under .50`,
    less_than_1 = `Estimate; Total: - .50 to .99`,
    less_than_1.25 = `Estimate; Total: - 1.00 to 1.24`,
    less_than_1.5 = `Estimate; Total: - 1.25 to 1.49`
    ) %>% 
  mutate(
    low_income = (less_than_50 + less_than_1 + less_than_1.25 + less_than_1.5) /
    low_inc_population
    )

pc_unemp_data<-read_csv("input data/qp_input_data/ACS_14_5YR_S2301_with_ann.csv",skip=1)
pc_unemp_data%<>%
  select(Id2, 
         unemp_population = `Total; Estimate; Population 16 years and over`,
         unemployed = `Unemployment rate; Estimate; Population 16 years and over`)
pc_unemp_data$unemployed = as.numeric((pc_unemp_data$unemployed))

#Joining Data
pc_data = left_join(pc_ed_data, pc_health_data, by = "Id2")
pc_data = left_join(pc_data, pc_low_inc_data, by = "Id2")
pc_data = left_join(pc_data, pc_unemp_data, by = "Id2")

#Scaling PCTs
pc_data = pc_data %>%
  mutate(low_income = low_income*100, bachelors_degree = bachelors_degree*100, 
         no_hs_degree = no_hs_degree*100)

##creating FIPS codes by taking only first 5 digits of tract codes
FIPS = substr(pc_data$Id2, 1,5)
FIPS = as.numeric(FIPS)
pc_data = cbind(pc_data, FIPS)
pc_data$FIPS[pc_data$FIPS == 10730] <- 1073
pc_data$FIPS[pc_data$FIPS == 29189] <- "MERGED" #setting both St. Louis county and city to FIPS = 0
pc_data$FIPS[pc_data$FIPS == 29510] <- "MERGED"
pc_data = filter(pc_data, !(health_population < 2 |
                              low_inc_population == 0))

#Creating Z-scores
pc_mpi_data = pc_data %>%
  group_by(FIPS)%>%
  mutate(z_low_income = NormZ(low_income),
         z_unemployed = NormZ(unemployed),
         z_no_hs_degree = NormZ(no_hs_degree),
         z_uninsured = NormZ(uninsured),
         z_overall = (z_low_income+z_unemployed+z_no_hs_degree+z_uninsured)/4)



##only the data needed for next part
#Health population was originally chosen as the population estimate in the 
#CCU15 Poverty Report. In the reproduction code it is named 'population.x.x'
mpi_data = pc_mpi_data %>%
  select(Id2, FIPS, mpi = z_overall, population = health_population)

##IDing mpi poor neighborhoods and extreme mpi poor neighborhoods
mpi_data$mpi_nh = NA
mpi_data$mpi_nh = "no"
mpi_data$mpi_nh[mpi_data$mpi > 1] = "yes"
mpi_data$mpi_nh = as.factor(mpi_data$mpi_nh)
mpi_data$ex_mpi_nh = NA
mpi_data$ex_mpi_nh = "no"
mpi_data$ex_mpi_nh[mpi_data$mpi > 2.5] = "yes"
mpi_data$ex_mpi_nh = as.factor(mpi_data$ex_mpi_nh)

##grouping by cities
mpi_city = mpi_data %>%
  group_by(FIPS) %>%
  dplyr::summarize(pop_mpi = sum(population[mpi_nh == "yes"]),
                   pop_ex_mpi = sum(population[ex_mpi_nh == "yes"]),
                   population = sum(population)
  ) 

#Computing Population living in MP
mpi_city = mpi_city %>%
  mutate(percent_in_mpi = 100*pop_mpi/population,
         percent_in_ex_mpi = 100*pop_ex_mpi/population) %>%
  arrange(percent_in_mpi)%>%
  select(-population)
mpi_city$year = 2014
mpi_city$FIPS = as.character(mpi_city$FIPS)

qp_data_fips = left_join(qp_data_fips, mpi_city, by = c("FIPS", "year"))
```

Volunteer Data Analysis
```{r}
#Reading in Data
v_2015 <- read_csv("input data/qp_input_data/volunteer2015.csv", progress = FALSE)

#Adding MSA codes
v_2015$MSA <- NA
v_2015$MSA[v_2015$CITY == "Birmingham-Hoover, AL"] = 13820
v_2015$MSA[v_2015$CITY == "Charlotte-Gastonia-Concord, NC-SC"] = 16740
v_2015$MSA[v_2015$CITY == "Cincinnati-Middletown, OH-KY-IN"] = 17140
v_2015$MSA[v_2015$CITY == "Columbus, OH"] = 18140
v_2015$MSA[v_2015$CITY == "Grand Rapids - Wyoming, MI"] = 24340
v_2015$MSA[v_2015$CITY == "Greensboro-High Point, NC"] = 24660
v_2015$MSA[v_2015$CITY == "Greenville, SC"] = 24860
v_2015$MSA[v_2015$CITY == "Indianapolis, IN"] = 26900
v_2015$MSA[v_2015$CITY == "Kansas City, MO-KS"] = 28140
v_2015$MSA[v_2015$CITY == "Knoxville, TN"] = 28940
v_2015$MSA[v_2015$CITY == "Louisville, KY-IN"] = 31140
v_2015$MSA[v_2015$CITY == "Memphis, TN-MS-AR"] = 32820
v_2015$MSA[v_2015$CITY == "Nashville-Davidson-Murfreesboro, TN"] = 34980
v_2015$MSA[v_2015$CITY == "Oklahoma City, OK"] = 36420
v_2015$MSA[v_2015$CITY == "Omaha-Council Bluffs, NE-IA"] = 36540
v_2015$MSA[v_2015$CITY == "St. Louis, MO-IL"] = 41180
v_2015$MSA[v_2015$CITY == "Tulsa, OK"] = 46140

v_2015$`2015` <- as.numeric(substr(v_2015$`2015`, 1, nchar(v_2015$`2015`)-1))
v_2015$`2015` <- as.numeric(v_2015$`2015`)
v_2015$Year <- NA
v_2015$Year <- 2015
v_2015%<>%dplyr::rename("volunteer_pct" = `2015`)%>%
  select(volunteer_pct, Year, MSA)

v_2014<-volunteer_read("~/Desktop/glp_website/input data/qp_input_data/volunteer2014.csv")
v_2013<-volunteer_read("~/Desktop/glp_website/input data/qp_input_data/volunteer2013.csv")
v_2012<-volunteer_read("~/Desktop/glp_website/input data/qp_input_data/volunteer2012.csv")
v_2011<-volunteer_read("~/Desktop/glp_website/input data/qp_input_data/volunteer2011.csv")

#Add City Names to 2015
key<-v_2014%>%
  select(MSA, city)
v_2015 <- left_join(v_2015, key, by = "MSA")

#Combining Datasets
v_data <- rbind(v_2011, v_2012)
v_data <- v_data %>%
  rbind(v_2013)%>%
  rbind(v_2014)%>%
  rbind(v_2015)
v_data$current <- 1
v_data%<>%dplyr::rename(year = Year)

#Create MSA Data
qp_data_msa <- v_data
```
Creating Map Data
```{r}

neighborhoods <- read_csv("~/Desktop/glp_website/map data/census tract neighborhoods.csv",col_types = cols(Id2 = col_character()))

mpi_data_maps <- left_join(mpi_data, neighborhoods, by = c("Id2"))
mpi_data_maps %<>% filter(FIPS == "21111")%>%
  select(-population)
```

```{r}
#White Data
white_dat <- read_csv("input data/qp_input_data/ACS_14_5YR_B02001_with_ann.csv", skip = 1)
white_dat %<>% select(Id, Id2, population = `Estimate; Total:`, 
                      white_pop = `Estimate; Total: - White alone`)%>%
  mutate(pct_white = white_pop/population)

FIPS = substr(white_dat$Id2, 1,5)
FIPS = data.frame(FIPS)
white_dat = bind_cols(white_dat, FIPS)
white_dat = filter(white_dat, FIPS == "21111" & population > 0 ) #Removes the airport

total <- white_dat%>%
  group_by(FIPS)%>%
  summarize(total_pop = sum(population), 
            total_white = sum(white_pop))%>%
  mutate(total_white_pct = total_white/total_pop)


white_dat$total_white_pct = 0.7317378

#Computing the "Difference Score"
white_dat %<>% mutate(dif_score = abs(pct_white - total_white_pct))%>%
  select(-population)

#Rescaling
white_dat$pct_white = white_dat$pct_white*100
white_dat$dif_score = white_dat$dif_score*100

map_data <- left_join(mpi_data_maps, white_dat, by = c("Id2", "FIPS"))
```

```{r}
#ACS Data Analysis
med_inc <- read_csv(
  "input data/qp_input_data/ACS_15_5YR_B19013_with_ann.csv",
  skip = 1,
  col_types = cols(Id2 = col_character(),
  Id = col_character())
  )

med_inc %<>% select(Id, Id2, median_income = `Estimate; Median household income in the past 12 months (in 2015 Inflation-adjusted dollars)`)

map_data <- map_data %>%
  left_join(., med_inc, by = c("Id2", "Id"))
```


Output Data
```{r}
write_csv(qp_data_fips, "~/Desktop/glp_website/output data/qp_data_fips.csv")
write_csv(qp_data_msa, "~/Desktop/glp_website/output data/qp_data_msa.csv")
write_csv(map_data, "~/Desktop/glp_website/map data/qp_map_data.csv")
```

To be continued...
